Title

### 2022-12-08 Article.tex
Write Section 1: Introduction

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.

@@

% Affiliations / Addresses (Add [1] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}

@@

% Abstract (Do not insert blank lines, i.e. \\) 
\abstract{A single paragraph of about 200 words maximum. For research articles, abstracts should give a pertinent overview of the work. We strongly encourage authors to use the following style of structured abstracts, but without headings: (1) Background: place the question addressed in a broad context and highlight the purpose of the study; (2) Methods: describe briefly the main methods or treatments applied; (3) Results: summarize the article's main findings; (4) Conclusions: indicate the main conclusions or interpretations. The abstract should be an objective representation of the article, it must not contain results which are not presented and substantiated in the main text and should not exaggerate the main conclusions.}

@@

\cite{Pantale-2022-EIN}
%\setcounter{section}{-1} %% Remove this when starting to work on the template.
%\section{How to Use this Template}
%The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section). Please check the instructions on the authors' page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX-related questions please contact latex@mdpi.com.%\endnote{This is an endnote.} % To use endnotes, please un-comment \printendnotes below (before References). Only journal Laws uses \footnote.
%% The order of the section titles is different for some journals. Please refer to the "Instructions for Authors” on the journal homepage.
%\section{Introduction}

>>>>

%---------
% pdftex
%---------
% The option pdftex is for use with pdfLaTeX. If eps figures are used, remove the option pdftex and use LaTeX and dvi2pdf.
\usepackage{gensymb}
\usepackage{amsmath}
\usepackage{accents}
\usepackage{multirow}
\usepackage{xspace}
\usepackage{subcaption}
\DeclareRobustCommand{\w}{\mbox{\large\ensuremath{\mathsf{w}}}}
\DeclareRobustCommand{\dotp}{\boldsymbol{\cdot}}
\DeclareRobustCommand{\e}[1]{{\rm e}^{#1}}
\DeclareRobustCommand{\lay}[1]{^{(#1)}}
\DeclareRobustCommand{\mdot}[1]{\accentset{\mbox{\bfseries .}}{#1}}
\DeclareRobustCommand{\ie}{\emph{i.e.}\@\xspace}
\DeclareRobustCommand{\eal}{et \emph{al.}\@\xspace}
\DeclareRobustCommand{\eg}{e.g.,\@\xspace}
\DeclareRobustCommand{\RMSE}{\text{E}_\text{RMS}}
\DeclareRobustCommand{\AARE}{\text{E}_\text{AAR}}
\DeclareRobustCommand{\R}{\text{R}}
\DeclareRobustCommand{\ps}{\text{s}^{-1}}
\DeclareRobustCommand{\mr}[2]{\multirow{#1}{*}{#2}}
\DeclareRobustCommand{\MPa}{\text{MPa}}

@@

% Affiliations / Addresses (Add [XX] after \address if there is only one affiliation.)
\address{%
$^{1}$ \quad Affiliation 1; e-mail@e-mail.com\\
$^{2}$ \quad Affiliation 2; e-mail@e-mail.com}

@@

% Abstract (Do not insert blank lines, i.e. \\)
\abstract{}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%\setcounter{section}{-1} %% Remove this when starting to work on the template.
%\section{How to Use this Template}
%
%The template details the sections that can be used in a manuscript. Note that the order and names of article sections may differ from the requirements of the journal (e.g., the positioning of the Materials and Methods section). Please check the instructions on the authors' page of the journal to verify the correct order and names. For any questions, please contact the editorial office of the journal or support@mdpi.com. For LaTeX-related questions please contact latex@mdpi.com.%\endnote{This is an endnote.} % To use endnotes, please un-comment \printendnotes below (before References). Only journal Laws uses \footnote.
%
%% The order of the section titles is different for some journals. Please refer to the "Instructions for Authors” on the journal homepage.
%

%------------------------------------------------------------------------------------
\section{Introduction}
%------------------------------------------------------------------------------------

Numerical methods for simulating the behavior of structures subjected to high thermomechanical loads, as in the case of high-temperature forming of metallic materials, are generally based on the use of commercial Finite Element (FE) codes such as Abaqus or laboratory codes such as DynELA \cite{Pantale-2004-DOF}, which has been developed at LGP for many years.
These simulation softwares are based on two types of equations: conservation equations and constitutive equations.
If the first equations are generally well established on the basis of physics and mechanics, it is not the same for the second type of equations: the constitutive equations.
Thus, in a general way, the conservation equations concern the fundamental principles of physics such as the mass conservation law, the momentum law (fundamental equation) and the energy law (declined in the form of the first and second principles of thermodynamics).
By themselves, these laws are not sufficient to describe the behavior of a material or a structure subjected to thermomechanical stresses, because the nature of the material's behavior, generally translated by means of the behavior laws, is not included in the system previously proposed.
Therefore, for each type of material, it is necessary to define behavior laws whose formulation is based on observation, in order to describe the behavior of this material under external stresses.
The quality and the accuracy of the results of any numerical simulation depend on the choice of these behavior laws and on the ability of the user to identify the coefficients of these behavior laws for a given material by performing experiments under conditions close to those encountered during the real stress of the structure in service that one wishes to design.
Depending on the nature of the stresses, these tests are based on quasi-static or dynamic tensile or compression tests, tests on thermomechanical simulators such as Gleeble or impact tests using gas launchers or Hopkinson bars.

Generally speaking, in the context of thermomechanical simulation of forming processes, these behavior laws define the dependence of the flow stress of the material $\sigma^y$ as a function of the three input variables which are the plastic strain $\varepsilon^p$, the strain rate $\mdot\varepsilon$ and the temperature $T$ of the material.
These laws, due to the nature of materials and the phenomena involved (work hardening, movement of dislocations, structural hardening, phase transformations, ...) are highly non-linear and their validity is restricted to a certain range of strains, strain rates and temperatures.
From the observations made, we can define two main classes of behavior laws: the flow laws based on physics and the empirical flow laws.
From the mechanics of continuous media and experimental tests and depending on the nature of the materials used, a number of flow models have been developed in the past, including: the Johnson-Cook flow law \cite{Johnson-1983}, the Zerilli Armstrong flow law \cite{Zerilli-1987} and their respective derived forms \cite{Rule-1998, Lin-2010, Li-2013, Zhang-2015, Zhou-2019}, the Hansel-Spittle \cite{Hensel-1978} or the Arrhenius \cite{Jonas-1969} flow laws, to name only a few of the most widely used in the context of the shaping of metallic materials at high temperature.
Once the choice has been made concerning the type of flow law to be used for a given material, it is then necessary, from a set of experimental tests carried out in the laboratory under conditions close to those of the structure in service, to identify the parameters of these flow laws by machine learning methods based on approaches of minimization of the calculated experiment.

The main problem that the researchers are confronted with after the phase of realization of the experimental tests concerns the choice of the flow law to use according to the observations made on these test results.
This choice of flow law is also restricted by the nature of the FE code used.
Thus, a user of the Abaqus FE code, will turn more particularly to a flow law of the Johnson-Cook \cite{Johnson-1983} type insofar as it is natively implemented in this software.
The choice of another form of flow law (Zerilli-Armstrong, or Arrhenius for example) obliges the user to program himself the computation of the flow stress $\sigma^y$ of the material by means of a VUMAT routine in FORTRAN as proposed by Liang \eal \cite{Liang-2022} for an Arrhenius type flow law.
The implementation of this VUMAT subroutine also requires the computation of the derivatives of the flow stress $\sigma^y$ with respect to the three input variables $\varepsilon^p$, $\mdot\varepsilon$ and $T$ which can quickly become relatively complex as the complexity of the flow law increases.
The choice of this flow law is therefore doubly guided by the nature of the behavior of the material on the one hand, but especially by the list of flow laws implemented natively in the FE codes.
At this time, there is not yet a flow law generic enough to cover a wide range of material behavior.

Depending on the nature of the study, the choice of this flow law is generally guided mainly by the list of flow laws available in the Finite Element code used, and very often this choice is made at the expense of the quality of the model.
For example, Zhou \eal \cite{Zhou-2019}, proposed the identification of the flow law of a GCr15 alloy for a continuous casting bloom with heavy reduction application.
In their study, they performed compression tests on GCr15 cylinders in a temperature range of $750~\celsius$ to $1300~\celsius$, strain rates of $0.001~\ps$ to $0.1~\ps$ and strains of $0$ to $0.7$.
The results of these compression tests, plotted in Figure \ref{fig:Zhou-OriginalData}, show a decrease in flow stress $\sigma^y$ with respect to temperature $T$ and a growth of $\sigma^y$ with respect to strain rate $\mdot\varepsilon$, as in most metallic materials.
\begin{figure}[!ht]
\centering
\includegraphics[width=0.9\columnwidth]{Figures/Zhou-OriginalData}
\caption{Original Data.}
\label{fig:Zhou-OriginalData}
\end{figure}
The evolution of the flow stress as a function of the plastic deformation shows the presence of a dynamic recrystallization phenomenon (DRX) within the material.
This phenomenon is an additional non-linearity of this type of material compared to other materials, mainly due to high temperatures and low strain rates, which should be taken into account when describing the material behavior.
As stated in their publication, depending on the flow model used: Johnson-Cook, Modified Zerilli-Armstrong, Arrhenius or new Modified Johnson-Cook, the fidelity of taking into account the real behavior varies widely with the complexity of the flow model which includes between $5$ parameters for the Johnson-Cook model, and up to $16$ parameters for the Arrhenius model.
Thus, and for the input data used, the two most common models: Johnson-Cook and Zerilli-Armstrong do not correctly describe the material behavior.
Only the modified Johnson-Cook and Arrhenius models are able to describe the behavior correctly.
Unfortunately, and this is not part of their study, if these last two models are satisfactory from a theoretical point of view, from a practical point of view for the user of a FE code such as Abaqus, it will be necessary to carry out a numerical implementation in a FORTRAN VUMAT subroutine of the modified Johnson-Cook flow law or the Arrhenius law as carried out by Liang \eal \cite{Liang-2022} in order to be able to use these laws for numerical simulation.
This requires a certain expertise in the development and implementation of flow laws, which is not available to all users of the Abaqus FE code.

From this observation, and from the necessity to select a flow law for a given type of material, then to identify the parameters of this flow law according to experimental tests, and finally to implement this flow law in the form of a user subroutine in FORTRAN in the Abaqus FE code, we have recently proposed in Pantalé \eal \cite{Pantale-2021} an alternative approach based on the ability of Artificial Neural Networks (ANNs) to behave as universal approximators.
The underlying idea is to implement a flow law described by an ANN in the form of a FORTRAN subroutine in the Abaqus FE code.
This neural network was previously trained from the data extracted from mechanical tests of the material and can directly define the value of the flow stress $\sigma^y$ as a function of the plastic strain $\varepsilon^p$, the strain rate $\mdot\varepsilon$ and the temperature $T$.
After this learning phase based on the use of the Python library Tensorflow \cite{Abadi-2016}, the weights and biases of the neural network are transcoded into a subroutine in FORTRAN which is compiled and linked with the libraries of the Abaqus FE code in order to include the behavior of the material by allowing the computation of the flow stress $\sigma^y$ as a function of $\varepsilon^p$, $\mdot\varepsilon$ and $T$, and of its three derivatives $\partial\sigma^y/\partial\varepsilon^p$, $\partial\sigma^y/\partial\mdot\varepsilon$ and $\partial\sigma^y/\partial T$.

The structure of this paper is as follows.
Section \ref{sec:Training} deals with the presentation of a Neural Network based flow law and its training from the data reported in figure \ref{fig:Zhou-OriginalData}.
The comparison of several neural network architectures regarding accuracy and implementation complexity will be presented.
In Section \ref{sec:Implementation}, we will present the conversion of this neural network into FORTRAN and C++ subroutines for Abaqus and DynELA FE codes.
Section \ref{sec:Simulations} will present real test cases of the use of an ANN flow law in numerical simulations and the comparison between the implementations made on Abaqus and DynELA.
Finally, a conclusion and perspective section will be presented at the end.

%------------------------------------------------------------------------------------
\section{Training of the ANN flow law}\label{sec:Training}
%------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------
\section{Implementation of the ANN flow law in FE softwares}\label{sec:Implementation}
%------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------
\section{Numerical simulations and benchmarks tests}\label{sec:Simulations}
%------------------------------------------------------------------------------------

%------------------------------------------------------------------------------------
\section{Conclusions and future work}\label{sec:Conclusions}
%------------------------------------------------------------------------------------
